Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
pass

This section discusses a sample of bugs reports. The selection
criteria we used was: (i) to cover all engines we found bugs--\chakra,
\jsc, and \veight, (ii) to cover each technique--test transplantation
and differential testing (with \radamsa\ and with \quickfuzz), (iii)
to cover a case of rejected bug report, and (iv) to use short tests
(for space).

@@

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
ascii}. The unary plus expression ``\CodeIn{+a}", used in the
assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN as result and the test fails
as expected. \chakra{}, instead, incorrectly converts the string
to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

>>>>

We issued several bug reports as result of this work. For space, we
are unable to discuss all of them. We sampled some bug reports to
discuss in the following. The selection criteria we used was: (i) to
cover all engines we found bugs--\chakra, \jsc, and \veight, (ii) to
cover each technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
rejected bug report, and (iv) to use short tests (for space).

@@

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character
(\CodeIn{NUL})\Comment{ in ascii}. The unary plus expression
``\CodeIn{+a}", used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN and the test fails as
expected. \chakra{}, instead, incorrectly converts the string to zero,
and the test passes. As Table~\ref{tab:bugs} shows, the \chakra{} team
fixed the issue soon after our report.

\Mar{--------------- estou aqui}
